---
title: "#Chapter 13 Relational Data"
author: "Brianna Cabrera"
output: html_notebook
---


```{r}
library(tidyverse)
library(nycflights13)
```
##13.2.1 Exercises

###1
You would need the `airports`,`planes`, and `flights` variables. The two tables you would need to combine are `airports` and `flights`.

###2
```{r}
colnames(weather)
colnames(airports)
```
The two tables can be matches by the variables `origin` in `weather` and `faa` in `airports`.

###3
It would allow us to match the weather to different destinations as well. 

###4
To represent that data as a data frame, we can create a table that contains the information of the special dates. The primary keys of that table would be `year`, `month`, and `day`.

##13.3.1Exercises

###1
```{r}
flights %>%
  mutate(index = row_number()) %>%
  select(index, everything())
```

###2

1. The primary keys for `Lahman::Batting` are `playerID`, `yearID`, `stint`, `teamID`, and `lgID`.
```{r}
Lahman::Batting %>%
  group_by(playerID, yearID, stint, teamID, lgID) %>%
  mutate(n = n()) %>%
  filter(n > 1) %>%
  nrow()
```
2. The primary keys for `babynames::babynames` are `year`, `sex`, `name`. 
```{r}
babynames::babynames %>%
  group_by(year, sex, name) %>%
  mutate(n = n()) %>%
  filter(n > 1) %>%
  nrow()
```
3. 

```{r}
#install.packages("nasaweather")
library(nasaweather)
nasaweather::atmos %>%
  group_by(lat, long, year, month) %>%
  mutate(n = n()) %>%
  filter(n > 1) %>%
  nrow()
```
The primary keys for `nasaweather::atoms` are `lat`, `long`, `year`, and `month`.


4. 
```{r}
#install.packages("fueleconomy")
library(fueleconomy)
fueleconomy::vehicles %>%
  group_by(id) %>%
  mutate(n = n()) %>%
  filter(n > 1) %>%
  nrow()
```

5. 
```{r}
install.packages("diamonds")
library(diamonds)
```
Couldn't load data set. 

###3
```{r}
install.packages("Lahamn")
library(Lahman)
```
Package not available.

##13.4.6 Exercises

###1
```{r}
airports %>%
  semi_join(flights, c("faa" = "dest")) %>%
  ggplot(aes(lon, lat)) +
    borders("state") +
    geom_point() +
    coord_quickmap()
```
```{r}
flights %>% group_by(dest) %>%
  summarize(avg_arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  left_join(airports, by = c('dest' = 'faa')) %>%
  ggplot(aes(x = lon, y = lat, size = avg_arr_delay, color = avg_arr_delay)) +
  borders('state') +
  geom_point() +
  coord_quickmap()
```

###2
```{r}
flights %>% 
  left_join(airports, by = c('dest' = 'faa')) %>%
  left_join(airports, by = c('origin' = 'faa'), suffix = c('.dest', '.origin')) %>%
  select(dest, origin, contains('lat'), contains('lon'))
```

###3
```{r}
flights %>% group_by(tailnum) %>%
  summarise(avg_dep_delay = mean(dep_delay, na.rm = TRUE),
            avg_arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  gather(key = 'mode', value = 'delay', 2:3) %>%
  left_join(planes, by = 'tailnum') %>%
  ggplot(mapping = aes(x = year, y = delay)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  facet_grid(.~mode)
```
It's hard to make a comparison.

###4
```{r}
flights %>% 
  left_join(weather, by = c('year','month','day','hour','origin')) %>%
  gather(key = 'condition', value = 'value', temp:visib) %>%
  filter(!is.na(dep_delay)) %>%
  ggplot(mapping = aes(x = value, y = dep_delay)) +
  geom_point() +
  facet_wrap(~condition, ncol = 3, scale = 'free_x')
```
There is not any strong correlation.

##13.5.1 Exercises

###1
```{r}
flights %>%
  filter(is.na(tailnum))
```

For a flight to have a missing `tailnum` means that that flight was cancelled. 
```{r}
flights %>%
  anti_join(planes, by = 'tailnum') %>%
  group_by(carrier) %>%
  summarize(n = n()) %>%
  arrange(desc(n))
```
The tail numbers that don't have a matching record in `planes` come from the same two carriers. 

###2
```{r}
flights %>%
  semi_join(count(flights, tailnum) %>% filter(n >= 100))
```

###3
```{r}
ten_common <-
  fueleconomy::common %>%
  ungroup() %>%
  arrange(-n) %>%
  top_n(10, n)
fueleconomy::vehicles %>%
  semi_join(ten_common)
```

###4
```{r}
fn <-flights %>%
  group_by(month, day) %>%
  summarize(avg_delay = sum(arr_delay + dep_delay, na.rm = TRUE)) %>%
  mutate(twoday_delay = avg_delay + lag(avg_delay)) %>%
  arrange(-twoday_delay)
wea <-weather %>%
  group_by(month, day) %>%
  summarize_at(vars(humid, precip, temp), mean, na.rm = TRUE)
fn %>%
  left_join(wea) %>%
  arrange(twoday_delay)
```

###5
It shows flights whose destinations are not included in the `airports` database. 
It shows the airport names and locations that the flights from `flights` are not flying to. 

###6
```{r}
flights %>%
  select(carrier, tailnum) %>%
  group_by(tailnum) %>%
  summarize(n = length(unique(carrier))) %>%
  filter(n > 1)
```
There were plants that were flown by over 1 carrier. 
